Additional analyses

### 2023-07-11 analyses_additional.Rmd
Major updates Implemented feedback

---
title: "Additional analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache = F)
options(digits = 3, width = 200, scipen=999)
```

 - Here you can find the code and the results of all additional analyses. 
 - To see the results, I recommend you directly go down to the Figures section. 
 - But if you're interested in how the analyses were executed, just tag along.
 - To see the code, click on button "Code". Alternatively, you can download the rmd file from the github repo.
 - To execute the code, first download the actual data from AUSSDA, then run analysis.rmd, then this file

@@

```{r r-setup, results='hide'}
# install packages
# devtools::install_github("https://github.com/tdienlin/td@v.0.0.2.5")

# define packages
packages <- c("broom.mixed", "brms", "devtools", "GGally", "ggplot2", 
              "gridExtra", "kableExtra", "knitr", "lavaan", "lme4", 
              "magrittr", "mice", "mvnormalTest", 
              "PerFit", "psych", "quanteda.textstats", "semTools", "tidyverse")

# load packages
lapply(c(packages, "td"), library, character.only = TRUE)

# load workspace
load("data/workspace_1.RData")
```

# Results with mean scores

Instead of using factor scores, in what follows I report the results with mean scores of affect. Note that the results for life satisfaction were the same, as it was measured with a single item.

## Positive affect

```{r}
model_aff_pos_lmer_m <- lmerTest::lmer(aff_pos_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long_imp)
summary(model_aff_pos_lmer_m)
```

The results differed only slightly, and all inferences remained the same.

## Negative Affect

```{r}
model_aff_neg_lmer_m <- lmerTest::lmer(aff_neg_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long_imp)
summary(model_aff_neg_lmer_m)
```

The results differed only slightly, and all inferences remained the same.

# Results without imputed data

We first need to export factor scores for variables without imputed data

```{r}
model <- "
aff_pos =~ a1*aff_pos_1 + a2*aff_pos_2 + a3*aff_pos_3
"
cfa_aff_pos <- cfa(model, d_long, group = "wave", estimator = "MLM")
d_long$aff_pos_fs <- get_fs(cfa_aff_pos)

model <- "
aff_neg =~ a1*aff_neg_1 + a2*aff_neg_2 + a3*aff_neg_3 + a4*aff_neg_4 + a5*aff_neg_5 + a6*aff_neg_6
"
cfa_aff_neg <- cfa(model, d_long, group = "wave", estimator = "MLM")
d_long$aff_neg_fs <- get_fs(cfa_aff_neg)
```

## Life satisfaction

```{r}
model_life_sat_lmer_noi <- lmerTest::lmer(life_sat ~
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long)
summary(model_life_sat_lmer_noi)
```

## Positive Affect

```{r}
model_aff_pos_lmer_noi <- lmerTest::lmer(aff_pos_fs ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long)
summary(model_aff_pos_lmer_noi)
```

## Negative Affect

```{r}
model_aff_neg_lmer_noi <- lmerTest::lmer(aff_neg_fs ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long)
summary(model_aff_neg_lmer_noi)
```

# Results with multiple imputation
## Life satisfaction

```{r}
model_life_sat_lmer_mim <- with(d_long_mim_mice, exp =  
                                lmerTest::lmer(life_sat ~
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      ))
model_life_sat_lmer_mim <- summary(pool(model_life_sat_lmer_mim), conf.int = TRUE)
```

## Positive Affect

For simplicity, note that we use mean-scores and not factors scores here.

```{r}
model_aff_pos_lmer_mim <- with(d_long_mim_mice, exp =  
                           lmerTest::lmer(aff_pos_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b)
)
model_aff_pos_lmer_mim <- summary(pool(model_aff_pos_lmer_mim), conf.int = TRUE)
```

## Negative Affect

For simplicity, note that we use mean-scores and not factors scores here.

```{r}
model_aff_neg_lmer_mim <- with(d_long_mim_mice, exp =  
                               lmerTest::lmer(aff_neg_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b)
)
model_aff_neg_lmer_mim <- summary(pool(model_aff_neg_lmer_mim), conf.int = TRUE)
```

# Figures

In what follows, see figure with all results combined.

## Activities

```{r}
# get data
dat_fig_results_activity <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, type = "activity", analysis = "1. regular")
dat_fig_results_activity_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, type = "activity", analysis = "2. no covars")
dat_fig_results_activity_m <- get_dat_res(model_aff_neg_lmer_m, model_aff_pos_lmer_m, model_life_sat_lmer, type = "activity", analysis = "3. mean scores")
dat_fig_results_activity_noi <- get_dat_res(model_aff_neg_lmer_noi, model_aff_pos_lmer_noi, model_life_sat_lmer_noi, type = "activity", analysis = "4. no imp")
dat_fig_results_activity_mim <- get_dat_res(model_aff_neg_lmer_mim, model_aff_pos_lmer_mim, model_life_sat_lmer_mim, type = "activity", analysis = "5. mult imp")

dat_fig_results_activity <- rbind(
  dat_fig_results_activity,
  dat_fig_results_activity_nco,
  dat_fig_results_activity_m,
  dat_fig_results_activity_noi,
  dat_fig_results_activity_mim
)
# make figure
fig_results_activity <- make_graph_res(
  dat_fig_results_activity,
  sesoi = "est"
  )
fig_results_activity

# safe figure
ggsave("figures/fig_results_activity.pdf", 
       width = 7, height = 4,
       plot = fig_results_activity)
```

## Channels

```{r}
# get data
dat_fig_results_channels <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, type = "channels", analysis = "1. regular")
dat_fig_results_channels_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, type = "channels", analysis = "2. no covars")
dat_fig_results_channels_m <- get_dat_res(model_aff_neg_lmer_m, model_aff_pos_lmer_m, model_life_sat_lmer, type = "channels", analysis = "3. mean scores")
dat_fig_results_channels_noi <- get_dat_res(model_aff_neg_lmer_noi, model_aff_pos_lmer_noi, model_life_sat_lmer_noi, type = "channels", analysis = "4. no imp")
dat_fig_results_channels_mim <- get_dat_res(model_aff_neg_lmer_mim, model_aff_pos_lmer_mim, model_life_sat_lmer_mim, type = "channels", analysis = "5. mult imp")

dat_fig_results_channels <- rbind(
  dat_fig_results_channels,
  dat_fig_results_channels_nco,
  dat_fig_results_channels_m,
  dat_fig_results_channels_noi,
  dat_fig_results_channels_mim
)
# make figure
fig_results_channels <- make_graph_res(
  dat_fig_results_channels,
  sesoi = "est"
  )
fig_results_channels

# safe figure
ggsave("figures/fig_results_channels.pdf", 
       width = 7, height = 4,
       plot = fig_results_channels)
```

Save results so that we can extract them in the manuscript.

```{r}
save.image("data/workspace_2.RData")
```

>>>>

---
title: "Additional analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache=T, max.row=20)
options(digits=2, width=260, scipen=999)
```

 - Here you can find the code and the results of all additional analyses. 
 - To see a good overview of the results, I recommend you directly go down to the Figures section. 
 - But if you're interested in how the analyses were executed, see below.
 - To see the code, click on button "Code". Alternatively, you can download the rmd file from the github repo.

@@

```{r r-setup, results='hide', cache=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td@v.0.0.2.5")

# define packages
library(broom.mixed)
library(brms)
library(devtools)
library(GGally)
library(ggplot2)
library(gridExtra)
library(kableExtra)
library(knitr)
library(lavaan)
library(lme4)
library(magrittr)
library(mice)
library(mvnormalTest)
library(PerFit)
library(psych)
library(quanteda.textstats)
library(semTools)
library(tidyverse)
library(td)

# load workspace
load("data/workspace_2.RData")
```

# Robustness analyses
## With additional covariates

These models include additional covariates that weren't preregistered and that weren't included, mainly because they are likely to be mediators. These are:

- Trust in ORF
- Trust in police
- Trust in parliament
- Trust in health sector
- Trust in government
- Trust in army

 - Media use: Kronen Zeitung oder www.krone.at
 - Media use: Der Standard oder derstandard.at
 - Media use: Die Presse oder diepresse.com
 - Media use: Oesterreich oder oe24.at
 - Media use: Kurier oder kurier.at
 - Media use: Salzburger Nachrichten oder salzburg.at
 - Media use: Sonstige oesterreichische Tageszeitungen
 - Media use: ORF (Nachrichten)
 - Media use: Privatfernsehen (Nachrichten)

### Life satisfaction

```{r}
model_life_sat_lmer_add <- "
  life_sat ~ 
    (1 | id) + (1 | wave) + 
    soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
    soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
    soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
    soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
    age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
    res_vienna + acc_bal + acc_gar + home_sqm + 
    corona_pos_b + corona_pos_w +
    work_h_b + work_h_w +
    work_homeoff_b +  work_homeoff_w +
    hh_income_b + hh_income_w +
    hh_adults + hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + 
    hh_oldfam + hh_outfam + hh_partner +
    home_owner +
    med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
    med_vid_orf_b + med_vid_pri_b + 
    med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + 
    med_vid_orf_w + med_vid_pri_w + 
    risk_prop_b + risk_prop_w + 
    act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
    act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
    sat_dem_w + sat_dem_b + 
    health_w + health_b +
    loc_cntrl_int_m_w + loc_cntrl_int_m_b +
    trst_media_w + trst_police_w + trst_media_w + trst_hlthsec_w + trst_gov_w + trst_army_w + 
    trst_media_b + trst_police_b + trst_media_b + trst_hlthsec_b + trst_gov_b + trst_army_b
"

fit_life_sat_lmer_add <- with(d_long_100_mim_mice, 
                              exp = lmerTest::lmer(model_life_sat_lmer_add))
fit_life_sat_lmer_add <- summary(pool(fit_life_sat_lmer_add), conf.int = TRUE)
print_res(fit_life_sat_lmer_add)
```

### Positive Affect

```{r}
model_aff_pos_lmer_add <- "
  aff_pos_m ~ 
    (1 | id) + (1 | wave) + 
    soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
    soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
    soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
    soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
    age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
    res_vienna + acc_bal + acc_gar + home_sqm + 
    corona_pos_b + corona_pos_w +
    work_h_b + work_h_w +
    work_homeoff_b +  work_homeoff_w +
    hh_income_b + hh_income_w +
    hh_adults + hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + 
    hh_oldfam + hh_outfam + hh_partner +
    home_owner +
    med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
    med_vid_orf_b + med_vid_pri_b + 
    med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + 
    med_vid_orf_w + med_vid_pri_w + 
    risk_prop_b + risk_prop_w + 
    act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
    act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
    sat_dem_w + sat_dem_b + 
    health_w + health_b +
    loc_cntrl_int_m_w + loc_cntrl_int_m_b +
    trst_media_w + trst_police_w + trst_media_w + trst_hlthsec_w + trst_gov_w + trst_army_w + 
    trst_media_b + trst_police_b + trst_media_b + trst_hlthsec_b + trst_gov_b + trst_army_b
"

fit_aff_pos_lmer_add <- with(d_long_100_mim_mice, 
                              exp = lmerTest::lmer(model_aff_pos_lmer_add))
fit_aff_pos_lmer_add <- summary(pool(fit_aff_pos_lmer_add), conf.int = TRUE)
print_res(fit_aff_pos_lmer_add)
```

### Negative Affect

```{r}
model_aff_neg_lmer_add <- "
  aff_neg_m ~ 
    (1 | id) + (1 | wave) + 
    soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
    soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
    soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
    soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
    age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
    res_vienna + acc_bal + acc_gar + home_sqm + 
    corona_pos_b + corona_pos_w +
    work_h_b + work_h_w +
    work_homeoff_b +  work_homeoff_w +
    hh_income_b + hh_income_w +
    hh_adults + hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + 
    hh_oldfam + hh_outfam + hh_partner +
    home_owner +
    med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
    med_vid_orf_b + med_vid_pri_b + 
    med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + 
    med_vid_orf_w + med_vid_pri_w + 
    risk_prop_b + risk_prop_w + 
    act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
    act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
    sat_dem_w + sat_dem_b + 
    health_w + health_b +
    loc_cntrl_int_m_w + loc_cntrl_int_m_b +
    trst_media_w + trst_police_w + trst_media_w + trst_hlthsec_w + trst_gov_w + trst_army_w + 
    trst_media_b + trst_police_b + trst_media_b + trst_hlthsec_b + trst_gov_b + trst_army_b
"

fit_aff_neg_lmer_add <- with(d_long_100_mim_mice, 
                              exp = lmerTest::lmer(model_aff_neg_lmer_add))
fit_aff_neg_lmer_add <- summary(pool(fit_aff_neg_lmer_add), conf.int = TRUE)
print_res(fit_aff_neg_lmer_add)
```

## Without control variables

Let's inspect how results change when control variables are omitted.

### Life satisfaction

```{r}
model_life_sat_lmer_nco <- "
  life_sat ~ 
    (1 | id) + (1 | wave) + 
    soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
    soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
    soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
    soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b
"
fit_life_sat_lmer_nco <- with(d_long_100_mim_mice, exp = lmerTest::lmer(model_life_sat_lmer_nco))
fit_life_sat_lmer_nco <- summary(pool(fit_life_sat_lmer_nco), conf.int = TRUE)
print_res(fit_life_sat_lmer_nco)
```

### Positive Affect

```{r}
model_aff_pos_lmer_nco <- "
  aff_pos_m ~ 
    (1 | id) + (1 | wave) + 
    soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
    soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
    soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
    soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b
"
fit_aff_pos_lmer_nco <- with(d_long_100_mim_mice, exp = lmerTest::lmer(model_aff_pos_lmer_nco))
fit_aff_pos_lmer_nco <- summary(pool(fit_aff_pos_lmer_nco), conf.int = TRUE)
print_res(fit_aff_pos_lmer_nco)
```

### Negative Affect

```{r}
model_aff_neg_lmer_nco <- "
  aff_neg_m ~ 
    (1 | id) + (1 | wave) + 
    soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
    soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
    soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
    soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b
"
fit_aff_neg_lmer_nco <- with(d_long_100_mim_mice, exp = lmerTest::lmer(model_aff_neg_lmer_nco))
fit_aff_neg_lmer_nco <- summary(pool(fit_aff_neg_lmer_nco), conf.int = TRUE)
print_res(fit_aff_neg_lmer_nco)
```

## Preregistered

Some changes were introduced because of feedback from colleagues (multiple imputation, imputation of all participants, inclusion of all variables). In what follows, please find the results as originally planned (but with some necessary deviations; for example not all preregistered variables could be included).

 - Use data-set in which participants with >50% data were removed. 
 - Also use factor scores (possible without multiple imputation).

Note that because here no multiple imputation was used, output looks differently.

### Life satisfaction

```{r}
model_life_sat_lmer_pre <- "
  life_sat ~ 
    (1 | id) + (1 | wave) + 
    soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
    soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
    soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
    soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
    age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
    res_vienna + acc_bal + acc_gar + home_sqm + 
    work_h_b + work_h_w +
    work_homeoff_b +  work_homeoff_w +
    hh_income_b + hh_income_w +
    hh_adults + hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + 
    hh_oldfam + hh_outfam + hh_partner +
    home_owner +
    med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
    med_vid_orf_b + med_vid_pri_b + 
    med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + 
    med_vid_orf_w + med_vid_pri_w + 
    risk_prop_b + risk_prop_w + 
    act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
    act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
    sat_dem_w + sat_dem_b + 
    health_w + health_b +
    loc_cntrl_int_m_w + loc_cntrl_int_m_b
    "
fit_life_sat_lmer_pre <- lmerTest::lmer(model_life_sat_lmer_pre, data = d_long_50_imp)
print_res(broom.mixed::tidy(fit_life_sat_lmer_pre, conf.int = T), imputation = FALSE)
```

### Positive Affect

```{r}
model_aff_pos_lmer_pre <- "
  aff_pos_fs ~ 
    (1 | id) + (1 | wave) + 
    soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
    soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
    soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
    soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
    age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
    res_vienna + acc_bal + acc_gar + home_sqm + 
    work_h_b + work_h_w +
    work_homeoff_b +  work_homeoff_w +
    hh_income_b + hh_income_w +
    hh_adults + hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + 
    hh_oldfam + hh_outfam + hh_partner +
    home_owner +
    med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
    med_vid_orf_b + med_vid_pri_b + 
    med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + 
    med_vid_orf_w + med_vid_pri_w + 
    risk_prop_b + risk_prop_w + 
    act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
    act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
    sat_dem_w + sat_dem_b + 
    health_w + health_b +
    loc_cntrl_int_m_w + loc_cntrl_int_m_b
    "
fit_aff_pos_lmer_pre <- lmerTest::lmer(model_aff_pos_lmer_pre, data = d_long_50_imp)
print_res(broom.mixed::tidy(fit_aff_pos_lmer_pre, conf.int = T), imputation = FALSE)
```

### Negative Affect

```{r}
model_aff_neg_lmer_pre <- "
  aff_neg_fs ~ 
    (1 | id) + (1 | wave) + 
    soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
    soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
    soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
    soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
    age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
    res_vienna + acc_bal + acc_gar + home_sqm + 
    work_h_b + work_h_w +
    work_homeoff_b +  work_homeoff_w +
    hh_income_b + hh_income_w +
    hh_adults + hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + 
    hh_oldfam + hh_outfam + hh_partner +
    home_owner +
    med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
    med_vid_orf_b + med_vid_pri_b + 
    med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + 
    med_vid_orf_w + med_vid_pri_w + 
    risk_prop_b + risk_prop_w + 
    act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
    act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
    sat_dem_w + sat_dem_b + 
    health_w + health_b +
    loc_cntrl_int_m_w + loc_cntrl_int_m_b
    "
fit_aff_neg_lmer_pre <- lmerTest::lmer(model_aff_neg_lmer_pre, data = d_long_50_imp)
print_res(broom.mixed::tidy(fit_aff_neg_lmer_pre, conf.int = T), imputation = FALSE)
```

## Without imputation

Final analysis, but now don't use any imputed data whatsoever. Was preregistered as additional analysis to provide comparison.

### Life satisfaction
